---
title: "ue5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# get the packages
```{r}
if(!require(install.load)){
  install.packages("install.load")
}
library(install.load)
```

```{r}
install_load("tidyverse")
```


# Load the datasets
```{r}
movies <- read_csv("movies.csv")
ratings <- read_csv("ratings.csv")
```

# Tasks for Today


## transform
First we get the average rating for each movie
```{r}
glimpse(movies)
head(movies)
glimpse(ratings)
```

```{r}
ratings["Count"] <- 1
mean_ratings <- ratings %>% group_by(movieId) %>% 
  summarise(Mean = mean(rating), "Number of Ratings" = sum(Count))

mean_ratings
```





## Join

Let's try out some join functions and see how they work on our two datasets
```{r}
movies_ratings_left <- left_join(movies, mean_ratings, by = "movieId")
movies_ratings_right <- right_join(movies, mean_ratings)
movies_ratings_inner <- inner_join(movies, mean_ratings)
movies_ratings_full <- full_join(movies, mean_ratings)
movies_ratings_anti <- anti_join(movies, mean_ratings)


# Which join is the most suitable for our usecase? Raise your hands!
```
```{r}
is.na(movies_ratings_full)
movies_ratings_right[is.na(movies_ratings_right), ]
```

## Analytics of our data

Which of the movies from High School Musical or Camp Rock has the best ratings?
```{r}
best_of_all_time <- movies_ratings_inner %>% 
  filter(substr(title, 1, 8) == "High Sch" | substr(title, 1, 8) == "Camp Roc") %>% 
  arrange(desc(Mean))

best_of_all_time

```

Let's get a selection of the best rated movies. We apply a filter to all movies that hit more than 100 ratings
```{r}
best_movies <- movies_ratiings_inner %>% 
  filter('Number of Ratings' > 100) %>% 
  arrange(desc(Mean))
head(best_movies)
```


Finally, we want to explore some bind functions
```{r}
c <- bind_rows(movies_ratings_left, movies_ratings_right)
c
```

```{r}
df <- tibble(num1 = 1:5, var1 = letters[1:5])
df <- tibble(vars)
```


